### 2020-06-18 Report/aws_325ghz_study.tex
A quick review of all existing text.

@@

\section{Introduction}
%
\subsection{Background}
The Arctic Weather Satellite (AWS) is a small platform carrying a single
radiometer package. This instrument is an across-track scanning microwave
radiometer. The exact channel configuration of AWS is not yet set. The main
issue for this report is that AWS will have channels at 183\,GHz, but also one
or several channels a higher frequencies. A number of channels around 325\,GHz
was considered as the main option before AWS became an ESA/EUMETSAT mission,
but it has now also been suggested to have a single channel at 229\,GHz. This
suggestion is based on MWS (MicroWave Sounder), one of the instruments onboard
the next generation of Metop satellites. The 229\,GHz was added to MWS as an
help for performing cloud screening of 183\,GHz data
\citep{rekha2012potential}. For comparison, it can be mentioned that ICI (Ice
Cloud Imager), another new Metop sensor, will include 325\,GHz channels.

\subsection{Aim}
%
To support the selection between 229 and 325\,GHz channels for AWS, this report
investigates the possibility to use the later range in forming 183\,GHz data of
``clear-sky'' character. That is, following \citet{rekha2012potential}, the
assumption, is that the 183\,GHz data will be used in an system not yet
capable of doing ``all -sky'' assimilation.

In \citet{rekha2012potential} the task was defined to screen out observations
having a cloud impact exceeding 4\,K at 183$\pm$7\,GHz. Their final suggestion
for screening does not involve data from any other channel than 229\,GHz, but
requires radiative transfer calculations (as a ``B-O test'' is made). Only 
screening of 183$\pm$7\,GHz was discussed.

@@

\subsection{Comparison to \citet{rekha2012potential}}
\label{sec:rekha}
%
Results from \citet{rekha2012potential} will be used as reference. They did not
suggest specific settings of their algorithm. The main consideration of the
scheme is a threshold value. We assume below 6\,K for
this value, as it used most frequently as example in
\citet{rekha2012potential}. According to their Table~3, this results in that
2.4\% of the ``cloudy'' cases are miss-classified as ``clear''. We assume that
these cases have a cloud impact of 4 to 8\,K (i.e.\ the screening is 100\%
successful for cloud impact above 8\,K). For a 6\,K threshold 41\% of the
``clear'' cases are classified as ``cloudy'' and a removed in the screening
process.

The selected threshold value is towards the high side of the ones considered by 
\citet{rekha2012potential}. A lower value improves the removal of ``cloudy'' cases,
but the fraction of incorrectly removed ``clear'' cases increases quickly. For
example, a threshold of 3\,K decreases the miss-classification of ``cloudy''
cases to 0.6\%, but increases the miss-classification for ``clear'' cases to 77\%.
If 183$\pm$7\,GHz is classified as cloudy, we assume that also the data from
other 183\,GHz channels are rejected.

@@

\subsection{Channel specifications}
%
The specifications of channels around 89, 166, 183 and 229\,GHz are assumed to
be fixed, with name, position and widths defined in Table~\ref{tab:fixed:chs}.
AWS channels 31 to 36 will be implemented as a single front-end, but are here
still considered as two ``bands'', denoted as 166 and 183\,GHz, to more easily
separate the channels in the text.

@@

\begin{table}[!b]
  \begin{minipage}[b]{0.5\linewidth}
  \centering  
  \begin{tabular}[c]{c|c|c}
    Channel & Frequency   & Bandwidth \\
    name    & [GHz] &  [MHz] \\
    \hline
    AWS-21  & \phantom{0}89.000 & 4000\\
    AWS-31  & 165.500 & 2800\\
    AWS-32  & 176.311 & 2000\\
    AWS-33  & 178.811 & 2000\\
    AWS-34  & 180.311 & 1000\\
    AWS-35  & 181.511 & 1000\\
    AWS-36  & 182.311 & \phantom{0}500\\
    AWS-4X  & 229.000 & 2000\\
    \hline
  \end{tabular}
  \end{minipage}%
  \begin{minipage}[b]{0.5\linewidth}
  \centering  
  \begin{tabular}[c]{c|c|c}
    Channel & Frequency   & Bandwidth \\
    name    & [GHz] &  [MHz] \\
    \hline
    ICI-5  & 325.15$\pm$9.50 & 3000\\
    ICI-6  & 325.15$\pm$3.50 & 2400\\
    ICI-7  & 325.15$\pm$1.50 & 1600\\
    \hline
  \end{tabular}
  \end{minipage}  
  \caption{Fixed channel position and widths. The left table covers channels of
    AWS, with values taken from SoW. Channels AWS-21 to AWS-36 are at this
    moment mandatory for AWS, while AWS-4X is so far tentative. The right table
    lists the values of some channels of ICI \citep{eriksson:towar:20}.}
  \label{tab:fixed:chs}
\end{table}

@@

\subsection{Radiative transfer simulations}
%
\subsubsection{ARTS}
%
All radiative transfer calculations are made by the Atmospheric Radiative
Transfer System (ARTS, \citet{eriksson:arts2:11,buehler:artst:18}), version
arts-2.3.????. Models and input used for absorption and hydrometeor properties
are described below. Ocean/water and land emissivities are taken from
TESSEM \citep{prigent2017sea} and TELSEM \citep{aires2011tool}, respectively.

Two calculations were performed for each atmospheric cases. One ''clear-sky''
where all hydrometeors contents were set to zero, and one ``all-sky'' where IWC
and RWC derived from CloudSat reflectivities and LWC from ERA-Interim were
included. Both sets of calculations were were made by ARTS's interface to the
RT4 solver \citep{evans1995microwavec}. This ``scattering solver'' was used
also for clear-sky, to avoid a possible bias between clear-sky and all-sky for
insignificant hydrometeor contents. RT4 handles the first two elements of the
Stokes vector, that were converted to brightness temperatures for H- and
V-polarisation.

@@

\subsection{Validation of simulations}
\label{sec:validation}
%
Using the simulation setup described above, around 77000 cases were simulated
based on randomly selected CloudSat orbits during August 2015. The input data
were restricted between $60^{\degree}$S to $60^{\degree}$N. No differentiation
was made between the observations over water and land.

@@

The overall agreement is good for channels. For 183 GHz channels (Channels
18-22), the simulations and observations have a good agreement for the part of
the PDFs matching clear-sky conditions (the main peak of the distribution),
albeit the simulations have a more sharp peak. This could either be caused by a
different geographical sampling of ATMS and CloudSat or to shortcomings in the
ERA-Interim input data. The fraction of cloudy observations is lower in ATMS in
comparison to simulations, for brightness temperatures below about 240\.K. This
is due to the fact that the antenna pattern is not considered in the
simulations.

In the intermediate region, the simulations have a lower occurrence rate. The
impact of hydrometeors should be somewhat higher in the upper sideband of ATMS,
which is not reflected in the simulations, but this is not sufficient to
explain the deviation. As this region is well covered in the simulations
reported in Fig.~7 of \citep{eriksson:towar:20}, the deviation of concern is
presumably also a consequence of the neglected antenna pattern. In this study,
this transitional region is of high interest. For this reason, the PDF for a
50\% random rejection of cases with an insignificant cloud impact is also
shown. This PDF gives a fair match in the intermediate region (but gives an
even higher overrepresentation at more strong cloud impacts). This smaller
dataset will be considered in parallel below, to ensure that no fraction of the
``cloudy'' cases is not underrepresentated in the results.

\section{Overview of the 183, 229 and 325\,GHz bands}
\label{sec:overview}
% 
The simulations in this section are based on five Fascod climate scenarios
(Sec.~\ref{sec:fascod}), and performed with a fixed sensor viewing angle of
25$^\circ$. No hydrometeors are included. For simpler interpretation of the
results, the reflectivity is set to have no frequency variation, i.e.\ the same
value is applied for all bands. The reflectivity is varied between 0 and 0.5
(these fixed values are only applied in this section, the bulk simulations are
using TESSEM and TELSEM for seting the surface properties).
In the figures covering transmissivities and Jacobians, the specifications
of ICI is applied for 325\,GHz channels (Table~\ref{tab:fixed:chs}).

@@

\begin{table}[!t]
  \centering  
  \begin{tabular}[c]{c|c|c|ccc}
    Channel & Frequency   & Bandwidth & $T_r=1200$\,K
    & $T_r=1800$\,K & $T_r=2400$\,K\\
    name    & [GHz] &  [MHz] & [K]  & [K] & [K]\\
    \hline
    AWS-41  & 325.15$\pm$6.50 & 3000 & 0.58 & 0.82 & 1.06 \\
    AWS-42  & 325.15$\pm$3.55 & 2500 & 0.64 & 0.90 & 1.16 \\
    AWS-43  & 325.15$\pm$1.60 & 1200 & 0.92 & 1.30 & 1.68 \\
    \hline
  \end{tabular}
  \caption{Tentative suggestion for a three 325\,GHz channels option. The
    values in the three last columns is the 1$\sigma$ noise level according to
    Eq.~\ref{eq:noise}, for $T_a=300$\,K and  $T_r$ }
  \label{tab:chs:prel3}
\end{table}

\begin{table}[!t]
  \centering  
  \begin{tabular}[c]{c|c|c|ccc}
    Channel & Frequency   & Bandwidth & $T_r=1200$\,K
    & $T_r=1800$\,K & $T_r=2400$\,K\\
    name    & [GHz] &  [MHz] & [K]  & [K] & [K]\\
    \hline
    AWS-41  & 325.15$\pm$6.60 & 2800 & 0.60 & 0.85 & 1.10 \\
    AWS-42  & 325.15$\pm$4.10 & 1800 & 0.75 & 1.06 & 1.37 \\
    AWS-43  & 325.15$\pm$2.40 & 1200 & 0.92 & 1.30 & 1.68 \\
    AWS-44  & 325.15$\pm$1.20 & \phantom{0}800 & 1.12 & 1.59 & 2.06\\
    \hline
  \end{tabular}
  \caption{Tentative suggestion for a four 325\,GHz channels option. Else as
    Table~\ref{tab:chs:prel4}.}
  \label{tab:chs:prel4}
\end{table}

@@

@@

\begin{table}[!h]
  \centering  
  \begin{tabular}[c]{c|c|c|ccc}
    Channel & Frequency   & Bandwidth & $T_r=1200$\,K
    & $T_r=1800$\,K & $T_r=2400$\,K\\
    name    & [GHz] &  [MHz] & [K]  & [K] & [K]\\
    \hline
    AWS-41  & 325.15$\pm$6.50 & 3000  & 0.58 & 0.82 & 1.06\\
    AWS-42  & 325.15$\pm$3.30 & 3000  & 0.58 & 0.82 & 1.06\\
    AWS-43  & 325.15$\pm$1.20 & \phantom{0}800 & 1.12 & 1.59 & 2.06\\
    \hline
  \end{tabular}
  \caption{The second three channel suggestion.}
  \label{tab:chs:3b}
\end{table}

@@

\begin{figure}[!tb]
  \centering
  \includegraphics[height=61mm]{fascod_3bchopt_tro}\hspace{5mm}% 
  \includegraphics[clip,trim=43 0 0 0,height=61mm]{fascod_3bchopt_mlw}
  \caption{RH weighting functions of the second three channel option
    (Table~\ref{tab:chs:3b}), for the Fascod tropical (left) and mid-latitude
    winter (right) scenarios.}
  \label{fig:3bch:prel}
\end{figure}

\section{Cloud correction by a simple scheme}
\label{sec:simple}
%
In this section, the 325\,GHz three channel option is evaluated for detection
and correction of cloud interference in 183\,GHz channels. Combinations of
brightness temperature (TB) differences between 183\,GHz and 325\,GHz are used
as a measure of the cloud impact. A regression based approach is used to
estimate the adjustment needed to predict the clear-sky values.

@@

The combinations of C1 and C2 are selected by matching their weighting
functions as shown in Fig.~\ref{fig:3ch:prel}. Five 183\,GHz and 325\,GHz paired
combinations are possible, for example one such paired combination is AWS-34
and AWS-42.

@@

We will simply treat cases that matches a correction below a certain value as
``clear-sky''. If the correction limit is denoted as $dtb_{cs}$, the threshold
value, $x_{cs}$, is obtained by inverting the polynomial fit:
\begin{equation}
x_{cs} = f_{cs}^{-1}(dtb_{cs}) 
\label{eq:dtb}
\end{equation}
That is, if $x_m>x_{cs}$ a measurement is classified as clear-sky. If
$x_m\leq x_{cs}$, the measurement is rejected if a pure filtering is made, or
it is adjusted if the correction scheme is applied. We will largely set
$dtb_{cs}$ based on the noise level of the 183\,GHz channel involved, to be
1$\sigma$ or 2$\sigma$ where $\sigma$ refers to the magnitude of measurement
noise (Eq.~\ref{eq:noise}, often called NE$\Delta$T). We will use $1\sigma$ for
the development of the scheme, however, the sensitivity of the scheme to
a 1$\sigma$ or 2$\sigma$ threshold is also provided later in the text.

\subsection{Application of correction scheme}
%
In this section, we test the applicability of the correction scheme in detail.
To analyse the performance of the approach, we apply it to correct the
measurements from C1 using data from C2. Without the availability of actual
data, the simulation dataset but with noise added is used mimic the measurements. The
noise for individual channels is calculated according to
Equation~\ref{eq:noise}. As an example, the results from the channel
combination AWS-34 and AWS-42 are shown. The error in the
predicted measurements is assessed as the deviation to corresponding noise-free
clear-sky value. The average bias, standard deviation and the measure of skewness, of the deviations are also calculated. Skewness gives a measure of asymmetry of the probability distribution of deviations around its mean.

@@

\begin{figure}[!tb]
	\centering
	\includegraphics[height=85mm]{PDF_corrected_AWS-34_AWS-42_allfits}
	\caption{Deviation of AWS-34 measurements to noise free clear-sky
      simulations before and after correction, corrected using a linear,
      quadratic and cubic model. The distribution of noise alone is also shown
      as reference. The measurements have been corrected using brightness
      temperatures from AWS-42. The clear/cloudy classification is made with $dtb_{cs} = 1\sigma$ and also cases with $Tb2 - Tb1 > -15$\,K are rejected.}
	\label{fig:correction:c34-42:fit}
\end{figure}
%
\begin{table}[!tb]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   skewness  & fraction  \\
		&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
		noise                     &   0.00 &  0.63 &               0.00 &                - \\
		uncorrected-all           &  -0.75 &  4.62 &             -11.78 &                - \\
		corrected-linear model    &  -0.03 &  0.75 &               0.48 &                2.84 \\
		corrected-quadratic model &  -0.06 &  0.71 &              -0.34 &                2.84 \\
		corrected-cubic model     &  -0.05 &  0.72 &              -0.23 &                2.84 \\
		\hline
	\end{tabular}
	\caption{Bias, standard deviation (std), and measure of skewness of error distributions
		shown in Figure~\ref{fig:correction:c34-42:fit}.The fraction rejected describes the percentage of cases which are removed. Results from three different fit models are shown: linear, quadratic and cubic.}
	\label{tab:correction:stats:34:42:allfits}
\end{table}
%
\begin{figure}[!tb]
	\centering
	\includegraphics[height=85mm]{PDF_corrected_AWS-34_AWS-42_thinned}
	\caption{Deviation of AWS-34 measurements to noise free clear-sky
      simulations before and after correction. The measurements have been
      corrected using a cubic model. The different datasets are: noise
      (simulation dataset), uncorrected (thinned measurements), filtered $1\sigma$ (cases classified as cloudy according to $dtb_{cs}$ = 1$\sigma$ are rejected), corrected $1\sigma$ (cases classified as cloudy according to $dtb_{cs}$ = 1$\sigma$ are corrected), corrected
      $2\sigma$ (cases classified as cloudy according to $dtb_{cs}$ = 2$\sigma$ are corrected), Sreerekha et al (cloudy cases are filtered according to \citet{rekha2012potential}).}
	\label{fig:correction:c34-42:thinned}
\end{figure}
%
\begin{table}[!tb]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   skewness  & fraction  \\
		&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
	noise             		&   0.00 &  0.63 &              -0.01 &                - \\
	uncorrected     		&  -1.27 &  6.05 &              -8.97 &                - \\
	filtered($1\sigma$)  	&  -0.13 &  0.68 &              -0.25 &               17.54 \\
	corrected($1\sigma$) 	&  -0.06 &  0.76 &              -0.46 &                4.99 \\
	corrected($2\sigma$) 	&  -0.11 &  0.75 &              -0.69 &                4.99 \\
	sreerekha et al   		&  -0.20 &  0.78 &              -1.00 &               45.36 \\			
		\hline
\end{tabular}
\caption{Bias, standard deviation (std), and measure of skewness of the
	error distributions of datasets shown in Figure~\ref{fig:correction:c34-42:thinned}.}
\label{tab:correction:stats:34:42:thinned}
\end{table}

@@

%
\subsection{Application of correction scheme using AWS-4X}
%
\begin{figure}[!t]
	\centering
	\includegraphics[height=85mm]{PDF_corrected_AWS-32_AWS-4X_thinned}
	\caption{Same as Fig.~\ref{fig:correction:c34-42:thinned}, but for channel combinations AWS-32 and AWS-4X. The dataset ``corrected 2$\sigma$'' is not shown.  }
	\label{fig:correction:c32-4X:thinned}
\end{figure}
%

@@

To develop the QRNN based correction scheme, we use the same dataset as in the simple scheme . Out of 125\,000 simulations, 90\% are used to train the model, while the rest 10\% is used to evaluate the model's performance during training. Presently we train QRNN for only nadir sensor viewing angle and the receiver noise $T_r$ = 1200\,K. In the training process, noise is added to the input according to Eqn~\ref{eq:noise}, every time the training data is exposed to the model. This ensures that the model is exposed to a new dataset on every iteration. Before training, the input data is normalized with mean and standard deviation.

@@

We train the QRNN to predict the quantiles $x_{\tau}$, for median, $\pm 1\sigma$, $\pm 2 \sigma$ and  $\pm 3 \sigma$ ($\tau$ = 0.002, 0.03, 0.16, 0.5, 0.84, 0.97, 0.998). The expectation value of the posterior distribution is assumed to be the best estimate for the predicted clear-sky value. To analyse the prediction accuracy, a testing dataset is constructed by randomly drawing 25\,000 cases from the simulation dataset. Noise is added to each simulation to mimic a new measurement dataset.

>>>>

[* IK: Run spell check just before submitting * ]

@@

\section{Introduction}
%
\subsection{Background}
The Arctic Weather Satellite (AWS) is a small platform carrying a single
radiometer package. This instrument is an across-track scanning microwave
radiometer. The exact channel configuration of AWS is not yet set. The main
issue for this study is that AWS will have channels at 183\,GHz, but also one
or several channels a higher frequencies. A number of channels around 325\,GHz
was considered as the main option before AWS became an ESA/EUMETSAT mission,
but it has now also been suggested to have a single channel at 229\,GHz. This
suggestion is based on MWS (MicroWave Sounder), one of the instruments onboard
the next generation of Metop satellites. The 229\,GHz was added to MWS as an
help for performing cloud screening of 183\,GHz data
\citep{rekha2012potential}. For comparison, it can be mentioned that ICI (Ice
Cloud Imager), another new Metop sensor, will include 325\,GHz channels.

\subsection{Aim}
%
To support the selection between 229 and 325\,GHz channels, this report
investigates the possibility to use the later range in forming 183\,GHz data of
``clear-sky'' character. That is, following \citet{rekha2012potential}, the
assumption, is that the 183\,GHz data will be used in an system not yet
capable of doing ``all -sky'' assimilation.

In \citet{rekha2012potential} the task was defined to screen out observations
having a cloud impact exceeding 4\,K at 183\,$\pm$\,7\,GHz. Their final suggestion
for screening does not involve data from any other channel than 229\,GHz, but
requires radiative transfer calculations (as a ``B-O test'' is made). Only 
screening of 183\,$\pm$\,7\,GHz was discussed.

@@

\subsection{Comparison to \citet{rekha2012potential}}
\label{sec:rekha}
%
Results from \citet{rekha2012potential} will be used as reference. They did not
suggest specific settings of their algorithm. The main consideration of their
scheme is a threshold value. We assume below 6\,K for
this value, as it used most frequently as example in
\citet{rekha2012potential}. According to their Table~3, this results in that
2.4\% of the ``cloudy'' cases are miss-classified as ``clear''. We assume that
these cases have a cloud impact of 4 to 8\,K (i.e.\ the screening is 100\%
successful for cloud impact above 8\,K). For a 6\,K threshold 41\% of the
``clear'' cases are classified as ``cloudy'' and a removed in the screening
process.

The selected threshold value is towards the high side of the ones considered by 
\citet{rekha2012potential}. A lower value improves the removal of ``cloudy'' cases,
but the fraction of incorrectly removed ``clear'' cases increases quickly. For
example, a threshold of 3\,K decreases the miss-classification of ``cloudy''
cases to 0.6\%, but increases the miss-classification for ``clear'' cases to 77\%.
If 183\,$\pm$7\,GHz is classified as cloudy, we assume that also the data from
other 183\,GHz channels are rejected.

@@

\subsection{Channel specifications}
%
The specifications of channels around 166, 183 and 229\,GHz are assumed to
be fixed, with name, position and widths defined in Table~\ref{tab:fixed:chs}.
AWS channels 31 to 36 will be implemented as a single front-end, but are here
still considered as two ``bands'', denoted as 166 and 183\,GHz, to more easily
separate the channels in the text.

@@

\begin{table}[!b]
  \begin{minipage}[b]{0.5\linewidth}
  \centering  
  \begin{tabular}[c]{c|c|c}
    Channel & Frequency   & Bandwidth \\
    name    & [GHz] &  [MHz] \\
    \hline
    AWS-31  & 165.500 & 2800\\
    AWS-32  & 176.311 & 2000\\
    AWS-33  & 178.811 & 2000\\
    AWS-34  & 180.311 & 1000\\
    AWS-35  & 181.511 & 1000\\
    AWS-36  & 182.311 & \phantom{0}500\\
    AWS-4X  & 229.000 & 2000\\
    \hline
  \end{tabular}
  \end{minipage}%
  \begin{minipage}[b]{0.5\linewidth}
  \centering  
  \begin{tabular}[c]{c|c|c}
    Channel & Frequency   & Bandwidth \\
    name    & [GHz] &  [MHz] \\
    \hline
    ICI-5  & 325.15$\pm$9.50 & 3000\\
    ICI-6  & 325.15$\pm$3.50 & 2400\\
    ICI-7  & 325.15$\pm$1.50 & 1600\\
    \hline
  \end{tabular}
  \end{minipage}  
  \caption{Fixed channel position and widths. The left table covers channels of
    AWS, with values taken from SoW. Channels AWS-31 to AWS-36 are at this
    moment mandatory for AWS, while AWS-4X is so far tentative. The right table
    lists the values of some channels of ICI \citep{eriksson:towar:20}.}
  \label{tab:fixed:chs}
\end{table}

@@

\subsection{Radiative transfer simulations}
%
\subsubsection{ARTS}
%
All radiative transfer calculations are made by the Atmospheric Radiative
Transfer System (ARTS, \citet{eriksson:arts2:11,buehler:artst:18}), version
arts-2.3.1284. Models and input used for absorption and hydrometeor properties
are described below. Ocean/water and land emissivities are taken from
TESSEM \citep{prigent2017sea} and TELSEM \citep{aires2011tool}, respectively.

Two calculations were performed for each atmospheric cases. One ''clear-sky''
where all hydrometeors contents were set to zero, and one ``all-sky'' where IWC
and RWC derived from CloudSat reflectivities and LWC from ERA-Interim were
included. Both sets of calculations were made by ARTS's interface to the
RT4 solver \citep{evans1995microwavec}. This ``scattering solver'' was used
also for clear-sky, to avoid a possible bias between clear-sky and all-sky for
insignificant hydrometeor contents. RT4 handles the first two elements of the
Stokes vector, that were converted to brightness temperatures for H- and
V-polarisation.

@@

\subsection{Validation of simulations}
\label{sec:validation}
%
Using the simulation setup described above, around 77000 cases [* Is this the
correct final number? *] were simulated
based on randomly selected CloudSat orbits during August 2015. The input data
were restricted between $60^{\degree}$S to $60^{\degree}$N. No differentiation
was made between the observations over water and land.

@@

The overall agreement is good for all channels. For 183 GHz channels (Channels
18-22), the simulations and observations have a good agreement for the part of
the PDFs matching clear-sky conditions (the main peak of the distribution),
albeit the simulations have a more sharp peak. This could either be caused by a
different geographical sampling of ATMS and CloudSat or to shortcomings in the
ERA-Interim input data. The fraction of cloudy observations is lower in ATMS in
comparison to simulations, for brightness temperatures below about 240\.K. This
is due to the fact that the antenna pattern is not considered in the
simulations.

In the intermediate region, the simulations have a lower occurrence rate. The
impact of hydrometeors should be somewhat higher in the upper sideband of ATMS,
which is not reflected in the simulations, but this is not sufficient to
explain the deviation. As this region is well covered in the simulations
reported in Fig.~7 of \citet{eriksson:towar:20}, the deviation of concern is
presumably also a consequence of the neglected antenna pattern. In this study,
this transitional region is of high interest. For this reason, the PDF for a
50\% random rejection of cases with an insignificant cloud impact is also
shown. This PDF gives a fair match in the intermediate region (but gives an
even higher overrepresentation at more strong cloud impacts). This smaller
dataset will be considered in parallel below, to ensure that no fraction of the
``cloudy'' cases is not underrepresentated in the results.

\subsection{Dataset formed}
%
[* Describe here briefly the final set of simulations used below. Number of
cases, with and without thinng. Latiude range. If the full dataset was used for
ATMS comparsion, switch place between 3.3 and 3.4. Probably easiest to say that
all results below are for nadir. Otherwise this has to be clarified for the
simple scehem. *]

\section{Overview of the 183, 229 and 325\,GHz bands}
\label{sec:overview}
% 
The simulations in this section are based on five Fascod climate scenarios
(Sec.~\ref{sec:fascod}), and performed with a fixed sensor viewing angle of
25$^\circ$ (deviation from nadir). No hydrometeors are included. For simpler
interpretation of the results, the reflectivity is set to have no frequency
variation, i.e.\ the same value is applied for all bands. The reflectivity is
varied between 0 and 0.5 (these fixed values are only applied in this section,
the bulk simulations are using TESSEM and TELSEM for seting the surface
properties). In the figures covering transmissivities and Jacobians, the
specifications of ICI is applied for 325\,GHz channels
(Table~\ref{tab:fixed:chs}).

@@

@@

\begin{table}[!p]
  \centering  
  \begin{tabular}[c]{c|c|c|ccc}
    Channel & Frequency   & Bandwidth & $T_r=1200$\,K
    & $T_r=1800$\,K & $T_r=2400$\,K\\
    name    & [GHz] &  [MHz] & [K]  & [K] & [K]\\
    \hline
    AWS-41  & 325.15$\pm$6.50 & 3000 & 0.58 & 0.82 & 1.06 \\
    AWS-42  & 325.15$\pm$3.55 & 2500 & 0.64 & 0.90 & 1.16 \\
    AWS-43  & 325.15$\pm$1.60 & 1200 & 0.92 & 1.30 & 1.68 \\
    \hline
  \end{tabular}
  \caption{Tentative suggestion for a three 325\,GHz channels option. The
    values in the three last columns is the 1$\sigma$ noise level according to
    Eq.~\ref{eq:noise}, for $T_a=300$\,K and stated $T_r$ }
  \label{tab:chs:prel3}
\end{table}

\begin{table}[!p]
  \centering  
  \begin{tabular}[c]{c|c|c|ccc}
    Channel & Frequency   & Bandwidth & $T_r=1200$\,K
    & $T_r=1800$\,K & $T_r=2400$\,K\\
    name    & [GHz] &  [MHz] & [K]  & [K] & [K]\\
    \hline
    AWS-41  & 325.15$\pm$6.60 & 2800 & 0.60 & 0.85 & 1.10 \\
    AWS-42  & 325.15$\pm$4.10 & 1800 & 0.75 & 1.06 & 1.37 \\
    AWS-43  & 325.15$\pm$2.40 & 1200 & 0.92 & 1.30 & 1.68 \\
    AWS-44  & 325.15$\pm$1.20 & \phantom{0}800 & 1.12 & 1.59 & 2.06\\
    \hline
  \end{tabular}
  \caption{Tentative suggestion for a four 325\,GHz channels option. Else as
    Table~\ref{tab:chs:prel4}.}
  \label{tab:chs:prel4}
\end{table}

\begin{table}[!p]
  \centering  
  \begin{tabular}[c]{c|c|c|ccc}
    Channel & Frequency   & Bandwidth & $T_r=1200$\,K
    & $T_r=1800$\,K & $T_r=2400$\,K\\
    name    & [GHz] &  [MHz] & [K]  & [K] & [K]\\
    \hline
    AWS-41  & 325.15$\pm$6.50 & 3000  & 0.58 & 0.82 & 1.06\\
    AWS-42  & 325.15$\pm$3.30 & 3000  & 0.58 & 0.82 & 1.06\\
    AWS-43  & 325.15$\pm$1.20 & \phantom{0}800 & 1.12 & 1.59 & 2.06\\
    \hline
  \end{tabular}
  \caption{The second three channel suggestion.}
  \label{tab:chs:3b}
\end{table}

\begin{figure}[!p]
  \centering
  \includegraphics[height=61mm]{fascod_3bchopt_tro}\hspace{5mm}% 
  \includegraphics[clip,trim=43 0 0 0,height=61mm]{fascod_3bchopt_mlw}
  \caption{RH weighting functions of the second three channel option
    (Table~\ref{tab:chs:3b}), for the Fascod tropical (left) and mid-latitude
    winter (right) scenarios.}
  \label{fig:3bch:prel}
\end{figure}

@@

@@

\section{Cloud correction by a simple scheme}
\label{sec:simple}
%
In this section, the (first) 325\,GHz three channel option is evaluated for detection
and correction of cloud interference in 183\,GHz channels. Combinations of
brightness temperature (TB) differences between 183\,GHz and 325\,GHz are used
as a measure of the cloud impact. A regression based approach is used to
estimate the adjustment needed to predict the clear-sky values.

@@

The combinations of C1 and C2 are selected by finding best match between
weighting functions. Five 183\,GHz and 325\,GHz combinations are possible, for
example one such paired combination is AWS-34 and AWS-42.

@@

We will simply treat cases that matches a correction below a certain value as
``clear-sky''. If the correction limit is denoted as $dtb_{cs}$, the threshold
value, $x_{cs}$, is obtained by inverting the polynomial fit:
\begin{equation}
x_{cs} = f_{cs}^{-1}(dtb_{cs}).
\label{eq:dtb}
\end{equation}
That is, if $x_m>x_{cs}$ a measurement is classified as clear-sky. If
$x_m\leq x_{cs}$, the measurement is rejected if a pure filtering is made, or
it is adjusted if the correction scheme is applied. We will largely set
$dtb_{cs}$ based on the noise level of the 183\,GHz channel involved, to be
1$\sigma$ or 2$\sigma$ where $\sigma$ refers to the magnitude of measurement
noise (Eq.~\ref{eq:noise}, often called NE$\Delta$T). We will use $1\sigma$ for
the development of the scheme, however, the sensitivity of the scheme to
a 1$\sigma$ or 2$\sigma$ threshold is also provided later in the text.

\subsection{Application of correction scheme}
%
In this section, we test the applicability of the correction scheme in detail.
To analyse the performance of the approach, we apply it to correct the
measurements from C1 using data from C2. Without the availability of actual
data, the simulation dataset but with noise added is used mimic the
measurements. The noise for individual channels is calculated according to
Equation~\ref{eq:noise}. As an example, the results from the channel
combination AWS-34 and AWS-42 are shown. The error in the predicted
measurements is assessed as the deviation to corresponding noise-free clear-sky
value. The average bias, standard deviation and the skewness of the
deviations are calculated. Skewness gives a measure of asymmetry of the
probability distribution of deviations around its mean.

@@

\begin{figure}[!tb]
	\centering
	\includegraphics[height=100mm]{PDF_corrected_AWS-34_AWS-42_allfits}
	\caption{Deviation of AWS-34 measurements to noise free clear-sky
      simulations before and after correction, corrected using a linear,
      quadratic and cubic model. The distribution of noise alone is also shown
      as reference. The measurements have been corrected using brightness
      temperatures from AWS-42. The clear/cloudy classification is made with $dtb_{cs} = 1\sigma$ and also cases with $Tb2 - Tb1 > -15$\,K are rejected.}
	\label{fig:correction:c34-42:fit}
\end{figure}
%
\begin{table}[!tb]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   skewness  & fraction  \\
		&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
		noise                     &   0.00 &  0.63 &               0.00 &                - \\
		uncorrected-all           &  -0.75 &  4.62 &             -11.78 &                - \\
		corrected-linear model    &  -0.03 &  0.75 &               0.48 &                2.84 \\
		corrected-quadratic model &  -0.06 &  0.71 &              -0.34 &                2.84 \\
		corrected-cubic model     &  -0.05 &  0.72 &              -0.23 &                2.84 \\
		\hline
	\end{tabular}
	\caption{Bias, standard deviation (std), and measure of skewness of error
      distributions shown in Figure~\ref{fig:correction:c34-42:fit}. The
      fraction rejected describes the percentage of cases which are removed.
      Results from three different fit models are shown: linear, quadratic and
      cubic.}
	\label{tab:correction:stats:34:42:allfits}
\end{table}
%
\begin{figure}[!tb]
  \centering \includegraphics[height=100mm]{PDF_corrected_AWS-34_AWS-42_thinned}
	\caption{Deviation of AWS-34 measurements to noise free clear-sky
      simulations before and after correction. The measurements have been
      corrected using a cubic model. The different datasets are: noise
      (simulation dataset), uncorrected (thinned measurements), filtered $1\sigma$ (cases classified as cloudy according to $dtb_{cs}$ = 1$\sigma$ are rejected), corrected $1\sigma$ (cases classified as cloudy according to $dtb_{cs}$ = 1$\sigma$ are corrected), corrected
      $2\sigma$ (cases classified as cloudy according to $dtb_{cs}$ = 2$\sigma$ are corrected), Sreerekha et al (cloudy cases are filtered according to \citet{rekha2012potential}).}
	\label{fig:correction:c34-42:thinned}
\end{figure}
%
\begin{table}[!p]
	\centering
	\begin{tabular}[b]{c|c|c|c|c}
		Dataset  		  &   bias &   std &   skewness  & fraction  \\
		&   [K]  &   [K] & [-] & rejected [\%]\\
		\hline
	noise             		&   0.00 &  0.63 &              -0.01 &                - \\
	uncorrected     		&  -1.27 &  6.05 &              -8.97 &                - \\
	filtered($1\sigma$)  	&  -0.13 &  0.68 &              -0.25 &               17.54 \\
	corrected($1\sigma$) 	&  -0.06 &  0.76 &              -0.46 &                4.99 \\
	corrected($2\sigma$) 	&  -0.11 &  0.75 &              -0.69 &                4.99 \\
	sreerekha et al   		&  -0.20 &  0.78 &              -1.00 &               45.36 \\			
		\hline
\end{tabular}
\caption{Bias, standard deviation (std), and measure of skewness of the error
  distributions of datasets shown in
  Figure~\ref{fig:correction:c34-42:thinned}.}
\label{tab:correction:stats:34:42:thinned}
\end{table}

@@

%
\subsection{Application of correction scheme using AWS-4X}
%

@@

To develop the QRNN based correction scheme, we use the same dataset as in the
simple scheme . Out of 125\,000 simulations, 90\% are used to train the model,
while the rest 10\% is used to evaluate the model's performance during
training. Presently we train QRNN for only nadir sensor viewing angle and the
receiver noise $T_r$ = 1200\,K. In the training process, noise is added to the
input according to Eq.~\ref{eq:noise}, every time the training data are exposed
to the model. This ensures that the model is exposed to a new dataset on every
iteration. Before training, the input data is normalized with mean and standard
deviation.

@@
